### 2021-07-15 src/paper/report.tex
Finish formatting of report and suppmat.

At the core of our agent-based model \citep[][we review more literature in Supplementary
Material~\ref{sec:literature_review}]{Aleta2020,Hinch2020} are physical contacts between
heterogeneous agents (Figure~\ref{fig:model_contacts_infections}) that potentially cause
infections. Contacts occur in up to four networks: Within the household, at
work, at school, or in other settings. Some contacts recur regularly, others occur at random.
Empirical applications can take the population and household structure from census data and the
network-specific frequencies of contacts from diary data measuring contacts before the
pandemic \citep[e.g.][]{Mossong2008,Hoang2019}. Within each network, meeting frequencies
depend on age and geographical location (see Supplementary
Material~\ref{subsec:assortativity}).

The four contact networks are chosen so that the most common NPIs can be modeled in
great detail. NPIs affect the number of contacts or the risk of transmitting the disease
upon having physical contact. The effect of different NPIs will generally vary across
contact types. See Section~\ref{sec:policies} for details on how we model NPIs.
In any setting, mask mandates or air filtes would reduce the probability
of infection \citep{Lessler2021, Cheng2021}.

@@

The model includes several other crucial features. New virus strains with different
infectiousness profiles may appear. Vaccines may become available. During the vaccine
roll-out, priority may depend on age and occupation; vaccine hesitancy is modelled by
some individuals refusing vaccination offers. With some probability, vaccinated agents
become immune and do not transmit the virus \citep{Hunter2021, LevineTiefenbrun2021,
Petter2021, Pritchard2021}.

@@

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and calibrate the model's many
parameters.\footnote{See Supplementary Material~\ref{sec:materials_and_methods} for a
    complete description.}
Examples are contact diaries, administrative records on case numbers, virus strains,
tests and vaccines as well as surveys on private rapid test demand.
Other studies' estimates of the seasonality of infections can be incorporated
directly. The remaining parameters---most notably, the infection probabilities
by contact network and the effects of some NPIs, see Supplementary
Material~\ref{subsec:estimated_params}---will be chosen numerically so that the model
matches features of the data \citep[see][for the general method]{McFadden1989}. By
modelling PCR and rapid tests in detail, we can translate infection numbers in the model
into observed infections before matching them to the data. The mechanism is
depicted in Figure~\ref{fig:model_official_cases} and described in Supplementary
Material~\ref{sub:testing}. Figure~\ref{fig:share_known_cases_by_age_group}
shows the resulting share of detected cases.

@@

    \floatfoot{\noindent \textit{Note:} The blue line in
        Figure~\ref{fig:2021_scenarios_recorded} is the same as in
        Figure~\ref{fig:aggregated_fit} and refers to our baseline scenario, so does the
        blue line in Figure~\ref{fig:2021_scenarios_newly_infected}. The red lines refer
        to a situation where NPIs evolve as in the baseline scenario and the B.1.1.7
        variant is introduced in the same way; vaccinations, rapid tests, and
        seasonality remain at their January levels. The other scenarios turn each of
        these three factors on individually. The decompositions in
        Figures~\ref{fig:2021_scenarios_decomposition} and
        \ref{fig:2021_scenarios_decomposition_tests} are based on Shapley values, which
        are explained in Appendix~\ref{sub:shapley_value}.
        All lines are rolling 7-day averages.}
\end{figure}

@@

Seasonality has a large effect in slowing the spread of SARS-CoV-2. By May 31, both
observed and total cases would be reduced by a factor of four if only seasonality
mattered. However, in this period, cases would have kept on rising throughout, just at a
much lower pace \citep[this is in line with results in][, which our seasonality measure
is based on]{Gavenciak2021}. Nevertheless, we estimate seasonality to be an
important factor, explaining most of the early changes and 43\% of the cumulative
difference by the end of May.

@@

% Despite the fact that only 10\% of the
% population performed weekly rapid tests in March on average, new infections on April~1
% would have been reduced by 53\% relative to the scenario without vaccinations, rapid
% tests, or seasonality.

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests and the main specification into the three channels for
rapid tests. Tests at schools have the smallest effect, which is largely explained by
schools not operating at full capacity during our period of study and the relatively
small number of students.\footnote{18\% of our population are in the education sector
    (pupils, teachers, etc.); 46\% are workers outside the education sector.} Almost 40\%
come from tests at the workplace. Despite the fact that rapid tests for private reasons
are phased in only in mid-March, they make up for more than half of the total effect.
The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. This is essentially a form of contact
tracing, which has been shown to be very effective \citep{Contreras2021,
    Fetzer2021,Kretzschmar2020}. Indeed, a deeper analysis in Supplementary
Material~\ref{subsec:appendix_scenarios} shows that the same amount of rapid tests
administered randomly in the population would not have been nearly as effective and that
mandatory tests at schools almost offset the increased infection risk of opening
schools (see Figure~\ref{fig:school_scenarios}).

Our analysis has shown that during the transition to high levels of vaccination and
possibly thereafter, large-scale rapid testing can substitute for some NPIs. This comes
at a fraction of the cost. A day of strict lockdown is
estimated to have cost around 50~Euros per capita \citep{Dorn2020b}; retail
prices for rapid tests were below one Euro in early June 2021. Widespread availability
of self-administered tests at low prices are likely to play a role for indication-driven
testing. Mandatory tests in schools and at the workplace are important to screen the
entire population. Especially, because disadvantaged groups are less likely to be
reached by testing campaigns relying on voluntary participation
\citep[e.g.][]{StillmanTonin2021}; at the same time,
these groups have a higher risk to contract CoViD-19 \citep{KochInstitut2021a}.
Compared to vaccinations, rapid testing programmes allow a much quicker roll-out, making
it arguably the most effective tool to contain the pandemic in the short run.

>>>>

At the core of our agent-based model \cite{Aleta2020,Hinch2020} (we review more
literature in Supplementary Material~\ref{sec:literature_review}) are physical contacts
between heterogeneous agents (Figure~\ref{fig:model_contacts_infections}) that
potentially cause infections. Contacts occur in up to four networks: Within the
household, at work, at school, or in other settings. Some contacts recur regularly,
others occur at random. Empirical applications can take the population and household
structure from census data and the network-specific frequencies of contacts from diary
data measuring contacts before the pandemic (e.g. \cite{Mossong2008,Hoang2019}). Within
each network, meeting frequencies depend on age and geographical location (see
Supplementary Material~\ref{subsec:assortativity}).

The four contact networks are chosen so that the most common NPIs can be modeled in
great detail. NPIs affect the number of contacts or the risk of transmitting the disease
upon having physical contact. The effect of different NPIs will generally vary across
contact types. See Section~\ref{sec:policies} for details on how we model NPIs. In any
setting, mask mandates or air filters would reduce the probability of infection
\citep{Lessler2021, Cheng2021}.

@@

The model includes several other crucial features. New virus strains with different
infectiousness profiles may appear. Vaccines may become available. During the vaccine
roll-out, priority may depend on age and occupation; vaccine hesitancy is modeled by
some individuals refusing vaccination offers. With some probability, vaccinated agents
become immune and do not transmit the virus \cite{Hunter2021, LevineTiefenbrun2021,
Petter2021, Pritchard2021}.

@@

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and calibrate the model's many
parameters.\footnote{See Supplementary Material~\ref{sec:materials_and_methods} for a
complete description.} Examples are contact diaries, administrative records on case
numbers, virus strains, tests and vaccines as well as surveys on private rapid test
demand. Other studies' estimates of the seasonality of infections can be incorporated
directly. The remaining parameters---most notably, the infection probabilities by
contact network and the effects of some NPIs, see Supplementary
Material~\ref{subsec:estimated_params}---will be chosen numerically so that the model
matches features of the data (see \cite{McFadden1989} for the general method). By
modelling PCR and rapid tests in detail, we can translate infection numbers in the model
into observed infections before matching them to the data. The mechanism is depicted in
Figure~\ref{fig:model_official_cases} and described in Supplementary
Material~\ref{sub:testing}. Figure~\ref{fig:share_known_cases_by_age_group} shows the
resulting share of detected cases.

@@

    \floatfoot{\noindent \textit{Note:} The blue line in
        Figure~\ref{fig:2021_scenarios_recorded} is the same as in
        Figure~\ref{fig:aggregated_fit} and refers to our baseline scenario, so does the
        blue line in Figure~\ref{fig:2021_scenarios_newly_infected}. The red lines refer
        to a situation where NPIs evolve as in the baseline scenario and the B.1.1.7
        variant is introduced in the same way; vaccinations, rapid tests, and
        seasonality remain at their January levels. The other scenarios turn each of
        these three factors on individually. The decompositions in
        Figures~\ref{fig:2021_scenarios_decomposition} and
        \ref{fig:2021_scenarios_decomposition_tests} are based on Shapley values, which
        are explained in Appendix~\ref{sub:shapley_value}. All lines are rolling 7-day
        averages.
    }
\end{figure}

@@

Seasonality has a large effect in slowing the spread of SARS-CoV-2. By May 31, both
observed and total cases would be reduced by a factor of four if only seasonality
mattered. However, in this period, cases would have kept on rising throughout, just at a
much lower pace (this is in line with results in \cite{Gavenciak2021}, which our
seasonality measure is based on). Nevertheless, we estimate seasonality to be an
important factor, explaining most of the early changes and 43\% of the cumulative
difference by the end of May.

@@

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests and the main specification into the three channels for
rapid tests. Tests at schools have the smallest effect, which is largely explained by
schools not operating at full capacity during our period of study and the relatively
small number of students.\footnote{18\% of our population are in the education sector
(pupils, teachers, etc.); 46\% are workers outside the education sector.} Almost 40\%
come from tests at the workplace. Despite the fact that rapid tests for private reasons
are phased in only in mid-March, they make up for more than half of the total effect.
The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. This is essentially a form of contact
tracing, which has been shown to be very effective \cite{Contreras2021,
Fetzer2021,Kretzschmar2020}. Indeed, a deeper analysis in Supplementary
Material~\ref{subsec:appendix_scenarios} shows that the same amount of rapid tests
administered randomly in the population would not have been nearly as effective and that
mandatory tests at schools almost offset the increased infection risk of opening schools
(see Figure~\ref{fig:school_scenarios}).

Our analysis has shown that during the transition to high levels of vaccination and
possibly thereafter, large-scale rapid testing can substitute for some NPIs. This comes
at a fraction of the cost. A day of strict lockdown is estimated to have cost around
50~Euros per capita \cite{Dorn2020b}; retail prices for rapid tests were below one Euro
in early June 2021. Widespread availability of self-administered tests at low prices are
likely to play a role for indication-driven testing. Mandatory tests in schools and at
the workplace are important to screen the entire population. Especially, because
disadvantaged groups are less likely to be reached by testing campaigns relying on
voluntary participation (e.g. \cite{StillmanTonin2021}); at the same time, these groups
have a higher risk to contract CoViD-19 \cite{KochInstitut2021a}. Compared to
vaccinations, rapid testing programmes allow a much quicker roll-out, making it arguably
the most effective tool to contain the pandemic in the short run.
